\apisummary{
    Creates a new set based on the input set and the triplet, which includes start \ac{PE} or index, size, and stride.
}

\begin{apidefinition}

\begin{Csynopsis}
int @\FuncDecl{shmem\_create\_set\_strided}@(shmem\_set\_t *parent\_set, int Index\_start, int Index\_stride, int size, shmem\_set\_t *new\_set);
\end{Csynopsis}

\begin{apiarguments}
     \apiargument{IN}{parent\_set}{A valid set. A valid set is either a pre-defined set or one created by application of one or more set creation operations.}
       \apiargument{IN}{index\_start}{The lowest PE index in the parent set, which will be part of new set.}
       \apiargument{IN}{PE\_index\_stride}{The integer displacement between the two consecutive PEs in the set.}
       \apiargument{IN}{PE\_size}{The number of PEs in the new set.}
     \apiargument{OUT}{new\_set}{An opaque handle representing the new set.}
\end{apiarguments}

\apidescription{
    The \FUNC{shmem\_create\_set\_strided} creates a new PE set from the \VAR{parent\_set} based on the triplet (\VAR{PE\_Start}, \VAR{PE\_stride}, and \VAR{PE\_size}) supplied to the routine. This is a local operation and can be called by any PE. Upon return from a call to the routine, a handle to the \VAR{new\_set} is allocated to all calling PEs. If the PE is a part of the \VAR{new\_set}, its index is a non-negative integer, otherwise it is negative. The \VAR{new\_set} contains the PE subset specified by the triplet. The indices of the \acp{PE} in the \VAR{new\_set} are ordered by their indices in \CONST{SHMEM\_SET\_WORLD}.
}

\apireturnvalues{
\FUNC{shmem\_create\_set\_strided}  returns 0 upon success; otherwise, it returns a non-zero value.
}

\apinotes{ The indices and \ac{PE} numbers are equivalent if the \VAR{parent\_set} is \CONST{SHMEM\_SET\_WORLD}.}

\end{apidefinition}
